Simulating a flock of birds

### 2017-10-28 tex/article.tex
conclusion

>>>>

\section{Conclusion}

In this paper we have presetend a model for studying the behaviour of interacting particles. The interaction between particles consisted in maintaining the average velocity of nearby neighbours. The system was studied when particles shared a common interaction radius and when each particle had a cone of vision. During the simulation it has been observed that the system goes through a phase transition where all particles assume the same direction. In order to describe the transition we have calculated the average normalized velocity va and investigated how it behaves when we modify the parameters of the system. In the thermodynamic limit va can be described using (5) or (6).
By plotting these equations we have found  the critical exponent $\beta$ to be equal to ....
